\documentclass{article}
\usepackage{graphicx}

\title{Software Design Document}
\author{}
\date{}

\begin{document}
\maketitle

\section{Introduction}

\subsection{Design Overview}
Give a description of the design approach, highlighting essential features that allow the design to meet the stated requirements.

\subsection{Requirements Traceability Matrix}
Provide a matrix showing where each feature identified in the SRS is supported by the design components.

\section{System Architectural Design}

\subsection{Chosen System Architecture}
Describe the system architectural design, identifying the major component groupings and the interfaces (both internal and external). Make sure to identify any significant technical risks, and identify contingency plans for each.

\subsection{Discussion of Alternative Designs}
Discuss in a reasonable level of detail other design options explored, and the reasons for not choosing them.

\subsection{System Interface Description}
Describe the system interfaces in detail: O/S interface, files, networking, libraries, graphics libraries etc.

\section{Detailed Description of Components}

\subsection{Component-n}
For each component, describe responsibilities, constraints, composition, interactions, and resources. Use appropriate diagrams or other notation to describe your design.

\section{User Interface Design}

\subsection{Description of the User Interface}
Describe the design of the user interface in detail.

\subsubsection{Screen Images}
Show the design of layout and menus for each screen.

\subsubsection{Objects and Actions}
Identify all the objects on each screen, and define the actions to be taken by each object for each event.

\section{System Architecture}

In this section high-level overview of how the functionality and responsibilities of the system were partitioned and then assigned to subsystems or components are provided.
Use cases from the SRS Document.

\section{Data Flow Specifications}

\subsection{Level 0 DFD with Description}
The Level 0 DFD provides an overview of the system's major processes and their interactions.

\subsection{Level 1 DFD with Description}
The Level 1 DFD elaborates on the processes identified in Level 0, breaking them down into more detailed subprocesses.

\end{document}
