\documentclass{article}

\begin{document}

\section*{Software Change Request Format}

\subsection*{1.0 Change Request Identification}

\subsubsection*{1.1 Name, Identification, and Description of Software Configuration Item(s):}
\begin{itemize}
  \item Software Configuration Item: Remote Wildlife Monitoring and Conservation Application (Version 1.0)
  \item Brief Description: A comprehensive application integrating drones, cameras, sensors, and data analytics for wildlife monitoring and conservation.
\end{itemize}

\subsubsection*{1.2 Requester and Contact Details:}
\begin{itemize}
  \item Requester: Dhairya
  \item Contact Details: abc@gmail.com
\end{itemize}

\subsubsection*{1.3 Date, Location, and Time When the Change is Requested:}
\begin{itemize}
  \item Date: 24 Jan 2024
  \item Location: KJSCE
  \item Time: 3:00
\end{itemize}

\subsection*{2.0 Description of the Change}

\subsubsection*{2.1 Description:}
\begin{itemize}
  \item \textbf{2.1.1 Background Information:} The project aims to enhance wildlife monitoring and conservation using technology.
  \item \textbf{2.1.2 Examples:} Supporting information includes the need for real-time data, challenges with traditional methods, and the scope of the project.
  \item \textbf{2.1.3 The Change:} Incorporating a more user-friendly interface for the Aerial Surveillance and Habitat Monitoring module.
\end{itemize}

\subsubsection*{2.2 Justification for the Change:}
\begin{itemize}
  \item Detailed justification: The current interface lacks user engagement and needs improvement for effective wildlife habitat monitoring.
\end{itemize}

\subsubsection*{2.3 Priority:}
\begin{itemize}
  \item Priority: High (Critical effect on system functionalities)
\end{itemize}

\section*{Software Change Report Format}

\subsection*{Change Report Identification}

\subsubsection*{1.1 Name, Identification, and Description of Software Configuration Item(s):}
\begin{itemize}
  \item Software Configuration Item: Remote Wildlife Monitoring and Conservation Application (Version 1.0)
  \item Brief Description: A comprehensive application integrating drones, cameras, sensors, and data analytics for wildlife monitoring and conservation.
\end{itemize}

\subsubsection*{1.2 Requester:}
\begin{itemize}
  \item Requester: Aarya
  \item Contact Details: xyz@gmail.com
\end{itemize}

\subsubsection*{1.3 Evaluator:}
\begin{itemize}
  \item Evaluator: Dhairya
\end{itemize}

\subsubsection*{1.4 Date and Time:}
\begin{itemize}
  \item Date and Time: 24 Jan 2024
\end{itemize}

\subsection*{2.0 Overview of Changes Required to Accommodate Request}

\subsubsection*{2.1 Description of Software Configuration Item that will be Affected:}
\begin{itemize}
  \item The Aerial Surveillance and Habitat Monitoring module.
\end{itemize}

\subsubsection*{2.2 Change Categorization:}
\begin{itemize}
  \item Type of Change: User Interface Enhancement.
\end{itemize}

\subsubsection*{2.3 Scope of the Change:}
\begin{itemize}
  \item \textbf{2.3.1 Technical Work Required:} Implementing a more user-friendly interface, including navigation and visualization improvements.
  \item \textbf{2.3.2 Technical Risks:} Minimal risks associated with UI changes.
\end{itemize}

\subsubsection*{3.0 Cost Assessment:}
\begin{itemize}
  \item Cost Assessment: Low (Primarily involves UI development time).
\end{itemize}

\subsubsection*{4.0 Recommendation}

\subsubsection*{4.1 Evaluator’s Recommendation:}
\begin{itemize}
  \item Recommendation: Approve the UI enhancement for the Aerial Surveillance and Habitat Monitoring module.
\end{itemize}

\subsubsection*{4.2 Internal Priority:}
\begin{itemize}
  \item Internal Priority: Medium (Important for improving user engagement and data accessibility).
\end{itemize}

\end{document}
