\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{array}
\usepackage{color}

\title{Risk Assessment and Risk Management Plan}
\author{Dhairya Satra | Aarya Tiwari}
\date{6th March 2024}

\begin{document}

\maketitle

\section*{Risk Assessment and Risk Management Plan}

\subsection*{Risk Assessment}
\begin{tabularx}{\textwidth}{|X|X|X|X|}
\hline
\textbf{Risk} & \textbf{Likelihood} & \textbf{Potential Impact} & \textbf{Risk Exposure} \\
\hline
Technological Failure of Drones & 5 & 8 & 40 \\
Data Privacy and Security & 7 & 9 & 63 \\
Legal and Regulatory Challenges & 6 & 7 & 42 \\
Environmental Impact & 4 & 7 & 28 \\
Stakeholder Engagement and Partnership Development & 5 & 6 & 30 \\
Technological Advancements and Market Changes & 6 & 8 & 48 \\
\hline
\end{tabularx}

\subsection*{Risk Management Plan}
\begin{itemize}[label={--}]

    \item Technological Failure of Drones:
    \begin{itemize}
        \item Regular maintenance and calibration of drones.
        \item Training drone operators on safety protocols and emergency procedures.
        \item Utilizing backup drones and technology.
    \end{itemize}
    \item Data Privacy and Security:
    \begin{itemize}
        \item Implementing strong encryption and authentication protocols.
        \item Regular security audits and vulnerability assessments.
        \item Ensuring compliance with data protection laws and regulations.
    \end{itemize}
    \item Legal and Regulatory Challenges:
    \begin{itemize}
        \item Staying updated with local and international regulations regarding drone operations.
        \item Engaging with regulatory bodies to address concerns and facilitate the project.
        \item Ensuring all drone operations are conducted within the legal framework.
    \end{itemize}
    \item Environmental Impact:
    \begin{itemize}
        \item Conducting environmental impact assessments before drone operations.
        \item Adopting sustainable practices for drone operations.
        \item Engaging with local communities and stakeholders to mitigate environmental concerns.
    \end{itemize}
    \item Stakeholder Engagement and Partnership Development:
    \begin{itemize}
        \item Establishing clear communication channels with stakeholders.
        \item Regular engagement and feedback sessions.
        \item Offering incentives for stakeholder involvement and partnership.
    \end{itemize}
    \item Technological Advancements and Market Changes:
    \begin{itemize}
        \item Conducting market research and staying updated with technological advancements.
        \item Being flexible and adaptable to changes.
        \item Investing in continuous learning and development for the project team.
    \end{itemize}
\end{itemize}

\subsection*{Risk Checklist}
\begin{tabularx}{\textwidth}{|X|X|X|}
\hline
\textbf{Risk} & \textbf{Risk Reduction Technique} & \textbf{Personal Shortfalls} \\
\hline
Unrealistic time and cost estimates & Multiple estimation techniques; design to cost; incremental development; recording and analysis of past projects; standardization of methods & Staffing with top talent; job matching; team building; training and career development; early scheduling of key personnel \\
Developing the wrong software function & Improved software evaluation; formal specification methods; user surveys; prototyping; early user manuals & Improved software evaluation; formal specification methods; user surveys; prototyping; early user manuals \\
Developing the wrong user interface & Prototyping; task analysis; user involvement & Prototyping; task analysis; user involvement \\
Gold plating & Requirement scrubbing; cost benefit analysis; design to cost & Requirement scrubbing; cost benefit analysis; design to cost \\
Late changes to requirements & Change control procedure; incremental development & Change control procedure; incremental development \\
Shortfalls in externally supplied components & Quality assurance procedures; competitive design or prototyping; contract incentives & Quality assurance procedures; competitive design or prototyping; contract incentives \\
Real-time performance shortfalls & Simulation; benchmarking; prototyping; tuning; technical analysis & Simulation; benchmarking; prototyping; tuning; technical analysis \\
Development technically too difficult & Staff training and development; prototyping; technical analysis & Staff training and development; prototyping; technical analysis \\
\hline
\end{tabularx}

\end{document}